%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Patsakorn Boonkerd} \\ \vspace{1pt}
    \footnotesize{
      \faIcon{envelope} \href{mailto:fordpatsakorn@gmail.com}{\underline{fordpatsakorn@gmail.com}} $|$ 
      % \faIcon{address-card} \href{https://fordkuppp.me/}{\underline{fordkuppp.me}} $|$ 
      \faIcon{linkedin} \href{https://www.linkedin.com/in/patsakorn-boonkerd/}{\underline{linkedin.com/in/patsakorn-boonkerd}} $|$
      \faIcon{github} \href{https://github.com/fordkuppp}{\underline{github.com/fordkuppp}} $|$
      \faIcon{phone} {\underline{+66 95 962 0846}}
    }
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {FlowAccount}{April 2025 -- Now}
    {Software Engineer (Infrastructure)}{Bangkok, Thailand}
    \resumeItemListStart
      \resumeItem{Provisioned and managed EKS clusters using Terraform, Terragrunt, FluxCD, and Karpenter.}
      \resumeItem{Deployed self-hosted GitHub Action Runners on EKS, reducing CI/CD costs by ~50\% compared to Buildjet.}
      \resumeItem{Configured External DNS, Gateway API, and External Secrets for DNS, ingress, and secret sync in EKS.}
      \resumeItem{Built GitHub Actions pipeline to generate AMIs with pre-pulled images, reducing EKS node startup time.}
      \resumeItem{Deployed ephemeral Jenkins on Kubernetes using JCasC, enabling declarative single-command provisioning.}
      \resumeItem{Migrated Jenkins freestyle jobs to Shared Libraries and Jenkinsfiles with Job DSL for version-controlled configs.}
      \resumeItem{Integrated Grafana and Prometheus for monitoring and observability within EKS clusters.}
      \resumeItem{Onboarded teams to create an alert system using JSM for real-time incident monitoring and response.}
      \resumeItem{Implemented a pseudo merge queue using GitHub Actions to streamline code integration processes.}
    \resumeItemListEnd

    \resumeSubheading
    {Agoda}{September 2024 -- March 2025 (6 months)}
    {Contract Software Developer (Backend)}{Bangkok, Thailand}
    \resumeItemListStart
      \resumeItem{Onboarded applications for disaster recovery by deploying to multiple datacenters using active-passive topology.}
      \resumeItem{Migrated Kotlin Spring framework application to use Kafka instead of RabbitMQ.}
      \resumeItem{Implemented client library for .NET Core application to avoid other services calling the API directly.}
      \resumeItem{Onboarded consumer and provider contract testing using Pact to validate client library migration.}
      \resumeItem{Implemented a kill switch for safe rollback during application migration in case of failure.}
    \resumeItemListEnd

    \resumeSubheading
      {Agoda}{August 2023 -- April 2024 (8 months)}
      {Software Engineer Intern (Backend)}{Bangkok, Thailand}
      \resumeItemListStart
        \resumeItem{Integrated code coverage tool into the GitLab CI pipeline to block any merge requests with insufficient tests.}
        \resumeItem{Migrated large .NET Framework legacy application to .NET Core and deployed to Istio service mesh.}
        \resumeItem{Developed new API endpoint using .NET Core to automate previously manual process.}
        \resumeItem{Automated email sending system to eliminate the need to manually send email to partners.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{Homelab} $|$ \emph{Kubernetes, Proxmox, Terragrunt, Docker, OpenTelemetry, Mimir, Grafana, SOPS, Tailscale}}{}
        \resumeItemListStart
          \resumeItem{Configured Proxmox, Kubernetes, and TrueNAS (RAIDZ1) on a personal server for scalable deployment.}
          \resumeItem{Developed Terragrunt modules to provision Proxmox VMs and LXC containers with cloud-init.}
          \resumeItem{Deployed Komodo via Terragrunt and cloud-init, syncing Docker Compose configs from Git for GitOps.}
          \resumeItem{Configured OpenTelemetry, Mimir, and Grafana to monitor resource usage across Proxmox VMs and hosts.}
          \resumeItem{Managed secrets using SOPS with age encryption, integrated with Bitwarden Secrets Manager.}
          \resumeItem{Enabled secure access and deployment with Tailscale and GitHub Actions.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Mahidol University International College}{Nakhon Pathom, Thailand}
      {Bachelor of Science in Computer Science, Minor in Japanese}{Sep. 2019 -- Jul. 2024}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Infrastructure}{: Kubernetes, EKS, Terraform, Terragrunt, Helm, Kustomize, FluxCD, Karpenter, Docker, Proxmox} \\
      \textbf{CI/CD \& Automation}{: GitHub Actions, GitLab CI/CD, Jenkins, Job DSL, JCasC} \\
      \textbf{Observability \& Networking}{: Grafana, Prometheus, OpenTelemetry, Mimir, External DNS, Gateway API} \\
      \textbf{Cloud \& Tools}{: AWS, SOPS, External Secrets, Kafka, RabbitMQ, Git, Bash, Unix} \\
      \textbf{Languages}{: Python, C\#, Java, SQL, HCL}
    }}
  \end{itemize}

%-----------ACTIVITIES-----------
% \section{Activities}
%     \resumeSubHeadingListStart
%       \resumeProjectHeading
%         {\textbf{Codegoda}}{April 2023}
%         \resumeItemListStart
%           \resumeItem{Attended Agoda hosted code competition}
%         \resumeItemListEnd
%     \resumeSubHeadingListEnd

%-----------LANGUAGES SKILLS-----------
\section{Languages Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Thai}{: Native} \\
     \textbf{English}{: C1 (IELTS 7.0)} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
